
---
title: "Telcom Churn -- Logistic model"
author: "Team ISSSR"

output: html_document:
toc: yes
---

```{r}
library(readr)
library(woe)
library(car)
require("randomForest")
require("ROCR")
#install.packages("neuralnet")
require(neuralnet)
#install.packages("nnet")
require(nnet)
require(ggplot2)
#install.packages("caret")
library(caret)
#install.packages("Metrics")
library(Metrics)
#install.packages("gbm")
library(gbm)
library(caTools)
#install.packages("e1071")
library(ROCR)
library(e1071)
library(caret)

#library(devtools)

#install.packages("woe")
library(woe)
#install.packages("devtools")
library(devtools)
#install.packages("riv")
library(riv) 

```

```{r}
churn <- read_csv("C:/Users/suyas/Downloads/Predictive - Shung/Predicitive Dataset/WA_Fn-UseC_-Telco-Customer-Churn.csv")
attach(churn)
```
## Add a new data column if output is categorical into numerical
```{r}

churn$churn_number <- 0
churn$churn_number[churn$Churn == 'Yes'] <- 1
#str(churn)
```


## Creating different bins for important variables and renaming them
```{r}
churn$tenure_M2M  <- (tenure * MonthlyCharges)
churn<-cbind(churn,class.ind(churn$InternetService))
names(churn)[names(churn)=="No"] <- "NoFibreOptic"
names(churn)[names(churn)=="DSL"] <- "Internet_DSL"
names(churn)[names(churn)=="Fiber optic"] <- "Internet_FiberOptic"


churn<-cbind(churn,class.ind(churn$OnlineSecurity))
names(churn)[names(churn)=="No"] <- "OnlineSecurity_No"
names(churn)[names(churn)=="Yes"] <- "OnlineSecurity_Yes"

churn<-cbind(churn,class.ind(churn$PaymentMethod))

churn<-cbind(churn,class.ind(churn$PhoneService))
names(churn)[names(churn)=="No"] <- "PhoneService_No"
names(churn)[names(churn)=="Yes"] <- "PhoneService_Yes"

churn<-cbind(churn,class.ind(churn$TechSupport))
names(churn)[names(churn)=="No"] <- "TechSupport_No"
names(churn)[names(churn)=="Yes"] <- "TechSupport_Yes"
names(churn)[names(churn)=="No internet service"] <- "TechSupport_No_Int"

churn<-cbind(churn,class.ind(churn$Contract))
names(churn)[names(churn)=="Month-to-month"] <- "Contract_MM"
names(churn)[names(churn)=="One year"] <- "Contract_OneYear"
names(churn)[names(churn)=="Two year"] <- "Contract_TwoYear"

churn<-cbind(churn,class.ind(churn$PaperlessBilling))
names(churn)[names(churn)=="No"] <- "PaperlessBilling_No"
names(churn)[names(churn)=="Yes"] <- "PaperlessBilling_Yes"

churn<-cbind(churn,class.ind(churn$Partner))
names(churn)[names(churn)=="No"] <- "Partner_No"
names(churn)[names(churn)=="Yes"] <- "Partner_Yes"


names(churn)[names(churn)=="Electronic check"] <- "Electronic_check_PM"

#str(churn)

```

## Breaking Tenure into sub groups
```{r}
churn$tenure_group<- NULL
group_tenure <- function(tenure)
  {
     x<- tenure
      if( x<12) {tenure_group<- 'tenure_group0_12'}
      else{
         if(x >= 12 & x<24) {tenure_group<- 'tenure_group12_24'}
         else{
            if(x >= 24 & x<48 ) {tenure_group<- 'tenure_group24_48'}
            else {tenure_group<-'tenure_group48_60'}
             }
      }
  }



churn$tenure_group <- sapply(churn$tenure,group_tenure)
#str(churn)
churn$tenure_group <- as.factor(churn$tenure_group)

churn<-cbind(churn,class.ind(churn$tenure_group))

```



## Data sampling ( partition into test and training dataset)
```{r}
set.seed(123)
sample = sample.split(churn$churn_number, SplitRatio = .75)
train = subset(churn, sample == TRUE)
test  = subset(churn, sample == FALSE)
nrow(train)
nrow(test)
#write.csv(train, "C:/Users/suyas/Downloads/Predictive - Shung/Project/Train.csv", row.names = FALSE)
#write.csv(test, "C:/Users/suyas/Downloads/Predictive - Shung/Project/Test.csv", row.names = FALSE)
```

## Build a Logistic Regression Model
```{r}
fit<- glm(train$churn_number ~ tenure * Contract_MM +
                Internet_FiberOptic+PaperlessBilling_Yes+Electronic_check_PM,
          family = binomial("logit"),
              data = train)
summary(fit)
```
## Feature anaylsis
```{r}
anova(fit, test="Chisq")
```


## train data predictions
```{r}
fit.result.train<-predict(fit,newdata=train,type='response')

fit.result.train<-ifelse(fit.result.train > 0.5,1,0)
misClasificError.train <- mean(fit.result.train != train$churn_number)
print(paste('Accuracy',1-misClasificError.train))
xtab<-  table(train$churn,fit.result.train)
confusionMatrix(xtab)

```
## AUC train data
```{r}
#str(train)
fit.results<-predict(fit,newdata = train)
auc(train$churn_number,fit.results)
```


##test data predictions
```{r}
fit.results.prob <- predict(fit,newdata=test)
fit.results.prob <- ifelse(fit.results.prob > 0.5,1,0)
misClasificError <- mean(fit.results.prob != test$churn_number)
print(paste('Accuracy',1-misClasificError))
#auc(test$churn_number,fit.results.prob)

xtest<-  table(test$churn,fit.results.prob)
confusionMatrix(xtest)


```

 
# AUC on test data, dont calculate it on the the actual predicted values rather on the probability, AUC on probability will decrease
```{r}
fit.results<-predict(fit,newdata = test)
auc(test$churn,fit.results)
```

## to check multicollinearity
```{r}
vif(fit)
```




## K fold Cross validation
```{r}
#str(train)
#train$churn_number <- as.factor(train$churn_number)
ctrl <- trainControl(method = "repeatedcv", number = 10, savePredictions = TRUE)

mod_fit <- train(churn_number ~ tenure+ tenure_M2M +
                Internet_FiberOptic+Contract_MM+PaperlessBilling_Yes+Electronic_check_PM, data=train, method="glm", family="binomial", trControl = ctrl, tuneLength = 5)

fit.results = predict(mod_fit, newdata=test)
fit.results.prob <- ifelse(fit.results.prob > 0.5,1,0)
misClasificError <- mean(fit.results.prob != test$churn_number)
print(paste('Accuracy',1-misClasificError))
confusionMatrix(fit.results.prob, test$churn_number)
auc(test$churn_number,fit.results)

```



